\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Dhruba Dutta Banik} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+919433433882 \\ Kolkata, West Bengal, India} 
\address{\href{mailto:dhrubaduttabanik@gmail.com.com}{dhrubaduttabanik@gmail.com} \\ \href{www.linkedin.com/in/dhruba-dutta-banik-963524231/}{www.linkedin.com/in/dhruba-dutta-banik-963524231/} \\ \href{www.github.com}{github.com/Dhruba2004}}  %
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Computer Science and Engineering Student seeking an Internship position to continue developing my skills and applying the knowledge I have learnt through my studies.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology in Computer Science and Engineering (IoT, Cybersecurity , Blockchain Technology }, 
University Of Engineering And Management,Kolkata \hfill {Expected 2026}\\


{\bf Class 12 WBCHSE}, Barasat PCS Govt.High School \hfill {2020 - 2022}
\item \textbf{Subjects:} {Computer Science, Chemistry, Physics, Math, English, Bengali}
    \hspace{1cm} \item \textbf{Marks:}   {84.8 \%}


{\bf Class 10 WBBSE}, Barasat PCS Govt.High School \hfill {2019 - 2020}
 \item \textbf{Subjects:} {Bengali, English, Math, History, Geography, Biology}
     \item \textbf{Marks:} {86.3 \%}



\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}


\begin{itemize}
\item {\textbf{Platforms :} {Windows, Linux}}
\item{\textbf{Languages :}  {C, C++, Python }}
\item{\textbf{Frontend :} {HTML, CSS , JS, React , tailwindcss}}
\item{\textbf{Backend :} {Node \& Express}}
\item{\textbf{DevOps :} {Git \& Github , Docker}}
\item{\textbf{IoT :} {Arduino}}
\end{itemize}



\end{rSection}

\begin{rSection}{Projects}
\vspace{-10px}
\item {\textbf{Metaverse-Website :} {A metaverse website made by nextjs , tailwind css and framer motion.}}
\item {\textbf{Dice Game :} {A simple dice game web application is made by HTML , CSS and JS.}}
\item {\textbf{Drum Kit :} {A simple drum kit web application is made by HTML , CSS and JS.}}
\item {\textbf{Personal Portfolio :} {personal portfolio website is made by React js}}
\end{rSection}


\begin{rSection}{Hobbies \& Interests} 
{Listening to Music}\par{Playing Video Games}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certified Courses} 

\begin{itemize}\item The MERN Fullstack Guide.
\end{itemize}
\begin{itemize}\item The Complete 2023 Web Development Bootcamp.
\end{itemize}
\begin{itemize}\item Amazon Web Services Cloud Practitioner.
\end{itemize}
\begin{itemize}\item Getting started with DevOps.
\end{itemize}
\begin{itemize}\item Ethical Hacking For beginners.
\end{itemize}
\end{rSection}


\end{document}
